Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review

### 2023-03-02 reports/revision_letter.Rmd
Address R1 comment 4

>>>>

Yes, we agree that the body of evidence does not lend itself to strong causal conclusions.
We note that we deliberately chose to avoid using strong causal language as much as possible, instead indicating that the evidence suggests associations with outcomes.
We have reread the manuscript and removed any remaining causal language that we found.
We have also added the following to the *Discussion* section:

`r revise::get_revision("r1_4")`

Note that we do use causal langauge when describing hypothesised mechanisms, and when describing guidelines.
We feel that this is sensible --- guidelines are based on causal assumptions, and while our evidence does not always support them, we are refering to them in the context that they are made (i.e., to instruct parents).
